---
title: "sideworksubset"
output: html_document
---

```{r}

```{r}
# Interaction models 

NIM1	<-	lm(formula = TD ~ AYTS * ATT * YDS * INT * `COMP%`, data = WP)
NIM2	<-	lm(formula = TT ~ CAY * IAY * `AGG%` * LCAD * ATT * TD * `COMP%`, data = WP)
NIM3	<-	lm(formula = CAY ~ IAY * AYD * LCAD * AYTS * YDS, data = WP)
NIM4	<-	lm(formula = IAY ~ CAY * AYD * YDS, data = WP)
NIM5	<-	lm(formula = AYD ~ CAY * IAY * AYTS * YDS, data = WP)
NIM6	<-	lm(formula = `AGG%` ~ TT * IAY * YDS * `COMP%`, data = WP)
NIM7	<-	lm(formula = LCAD ~ TT * CAY * YDS, data = WP)
NIM8	<-	lm(formula = AYTS ~ IAY * YDS * TD, data = WP)
NIM9	<-	lm(formula = ATT ~ TT * IAY * AYD * YDS * TD * INT * `COMP%`, data = WP)
NIM10	<-	lm(formula = INT ~ AYD * `AGG%` * ATT * TD * `COMP%`,   data = WP)
NIM11	<-	lm(formula = `COMP%` ~ TT * IAY * AYD * `AGG%` * ATT * YDS * TD * INT, data = WP)
NIM12	<-	lm(formula = TD ~ TT * CAY * `AGG%` * AYTS * YDS * INT * `COMP%`, data = NGSP)
NIM13	<-	lm(formula = TT ~ `AGG%` * YDS * TD * `COMP%`, data = NGSP)
NIM14	<-	lm(formula = CAY ~ TT * IAY * AYD, data = NGSP)
NIM15	<-	lm(formula = IAY ~ `AGG%` * LCAD * AYTS * `COMP%`,  data = NGSP)
NIM16	<-	lm(formula = `AGG%` ~ IAY * YDS * INT, data = NGSP)
NIM17	<-	lm(formula = LCAD ~ IAY * YDS, data = NGSP)
NIM18	<-	lm(formula = AYTS ~ IAY * TD, data = NGSP)
NIM19	<-	lm(formula = ATT ~ TT * CAY * `AGG%` * YDS * `COMP%`,  data = NGSP)
NIM20	<-	lm(formula = INT ~ `AGG%` * ATT * TD, data = NGSP)
NIM21	<-	lm(formula = `COMP%` ~ TT * AYD * `AGG%` * YDS * TD, data = NGSP)
NIM22	<-	lm(formula = Yds ~ Rec * Avg * TD * FUM, data = WRW)
NIM23	<-	lm(formula = Avg ~ Rec * Yds * TD, data = WRW)
NIM24	<-	lm(formula = TD ~ Rec * Yds * Avg * FUM, data = WRW)
NIM25	<-	lm(formula = FUM ~ Rec * Yds * TD, data = WRW)
NIM26	<-	lm(formula = Rec ~ Yds * Avg * TD * FUM, data = WRW)
NIM27	<-	lm(formula = YDS ~ CUSH * SEP * TAY * TAR * `CTCH%` * `YAC/R`,   data = ADVWRS)
NIM28	<-	lm(formula = CUSH ~ SEP * `TAY%` * `CTCH%` * YDS *  `YAC/R`, data = ADVWRS)
NIM29	<-	lm(formula = TAY ~ SEP * `TAY%` * TAR * `CTCH%` *  TD * `YAC/R`, data = ADVWRS)
NIM30	<-	lm(formula = SEP ~ CUSH * TAY * `CTCH%` * YDS * `YAC/R` * `xYAC/R`, data = ADVWRS)
NIM31	<-	lm(formula = `TAY%` ~ CUSH * TAY * `CTCH%` * YDS *  `YAC/R` * `xYAC/R`, data = ADVWRS)
NIM32	<-	lm(formula = REC ~ TAR * `CTCH%` * `xYAC/R`, data = ADVWRS)
NIM33	<-	lm(formula = TAR ~ TAY * `TAY%` * REC * `CTCH%` *  TD, data = ADVWRS)
NIM34	<-	lm(formula = `CTCH%` ~ CUSH * SEP * TAY * `TAY%` *   REC * TD * `YAC/R`, data = ADVWRS)
NIM35	<-	lm(formula = TD ~ TAY * `CTCH%` * YDS * `YAC/R` *  `xYAC/R`, data = ADVWRS)
NIM36	<-	lm(formula = TD ~ Att * Yds, data = RUSHW)
NIM37	<-	lm(formula = Att ~ Yds * Avg * TD, data = RUSHW)
NIM38	<-	lm(formula = Yds ~ Att * Avg * TD * FUM, data = RUSHW)
NIM39	<-	lm(formula = Avg ~ Att * Yds * FUM, data = RUSHW)
NIM40	<-	lm(formula = FUM ~ Yds * Avg, data = RUSHW)
NIM41	<-	lm(formula = TD ~ YDS, data = ADVRUSHS)
NIM42	<-	lm(formula = EFF ~ `8+D%` * TLOS * YDS * AVG * TD, data = ADVRUSHS)
NIM43	<-	lm(formula = TLOS ~ EFF * `8+D%` * AVG, data = ADVRUSHS)
NIM44	<-	lm(formula = `8+D%` ~ EFF * TLOS * AVG, data = ADVRUSHS)
NIM45	<-	lm(formula = ATT ~ EFF * YDS * AVG * TD, data = ADVRUSHS)
NIM46	<-	lm(formula = YDS ~ EFF * ATT * AVG * TD, data = ADVRUSHS)
NIM47	<-	lm(formula = AVG ~ EFF * `8+D%` * TLOS * TD, data = ADVRUSHS)
NIM48	<-	lm(formula = Sacks ~ `Sack Yds` * `QB Hits` * Tackles *   Assists * `Fumbles Forced`, data = DEF_W)
NIM49	<-	lm(formula = `Sack Yds` ~ Sacks * `QB Hits` * Assists *  `Fumbles Forced`, data = DEF_W)
NIM50	<-	lm(formula = `QB Hits` ~ Sacks * `Sack Yds` * Tackles *  Assists * `Fumbles Forced`, data = DEF_W)
NIM51	<-	lm(formula = Tackles ~ Sacks * `QB Hits` * Assists * `Fumbles Forced`, data = DEF_W)
NIM52	<-	lm(formula = Assists ~ Sacks * `Sack Yds` * `QB Hits` *  Tackles * `Fumbles Forced` * `Fumbles Recovered`,   data = DEF_W)
NIM53	<-	lm(formula = `Fumbles Forced` ~ Sacks * `Sack Yds` * `QB Hits` * Tackles * Assists * `Fumbles Recovered`, data = DEF_W)
NIM54	<-	lm(formula = `Fumbles Recovered` ~ Assists * `Fumbles Forced`, data = DEF_W)
NIM55	<-	lm(formula = Int ~ Tgt * TD * DADOT * Bltz * TC * TM2, data = ADVDEF)
NIM56	<-	lm(formula = Tgt ~ Int * Yds * TD * DADOT * Bltz * QBKD * Prss *   TC * TM2, data = ADVDEF)
NIM57	<-	lm(formula = Cmp ~ Int * Tgt * TD * DADOT * YAC * Bltz * Prss *  TC * TM2, data = ADVDEF)
NIM58	<-	lm(formula = Yds ~ Air * YAC, data = ADVDEF)
NIM59	<-	lm(formula = TD ~ Int * Yds * DADOT * YAC * TM2, data = ADVDEF)
NIM60	<-	lm(formula = DADOT ~ Int * Yds * TD * YAC * Bltz * Sk * Prss * TC, data = ADVDEF)
NIM61	<-	lm(formula = Air ~ Yds * YAC, data = ADVDEF)
NIM62	<-	lm(formula = YAC ~ Int * Cmp * TD * DADOT * Bltz * Hrry * QBKD *  TC * TM2, data = ADVDEF)
NIM63	<-	lm(formula = Bltz ~ Int * Cmp * TD * DADOT * YAC * QBKD * Sk * TC * TM2, data = ADVDEF)
NIM64	<-	lm(formula = Hrry ~ DADOT * YAC * Bltz * QBKD * Sk * TC * TM2,  data = ADVDEF)
NIM65	<-	lm(formula = QBKD ~ Bltz * Sk * Prss * TM2, data = ADVDEF)
NIM66	<-	lm(formula = Sk ~ Int * Bltz * QBKD * Prss * TM2, data = ADVDEF)
NIM67	<-	lm(formula = Prss ~ Int * TD * Bltz * Hrry * QBKD * Sk * TC, data = ADVDEF)
NIM68	<-	lm(formula = TC ~ Int * Cmp * DADOT * YAC * Bltz * Prss * TM2, data = ADVDEF)
NIM69	<-	lm(formula = TM2 ~ Int * TD * YAC * Bltz * Sk * Prss * TC, data = ADVDEF)
NIM70	<-	lm(formula = TD ~ CAY * AYTS * YDS * INT * `COMP%`, data = WP)
NIM71	<-	lm(formula = TT ~ IAY * `AGG%` * LCAD * ATT * TD * `COMP%`,  data = WP)
NIM72	<-	lm(formula = CAY ~ TT * IAY * LCAD * AYTS * TD * INT * `COMP%`,  data = WP)
NIM73	<-	lm(formula = IAY ~ CAY * `AGG%` * AYTS * ATT * TD * INT *  `COMP%`, data = WP)
NIM74	<-	lm(formula = `AGG%` ~ TT * AYTS * ATT * INT * `COMP%`, data = WP)
NIM75	<-	lm(formula = LCAD ~ TT * CAY * YDS, data = WP)
NIM76	<-	lm(formula = AYTS ~ TT * CAY * `AGG%` * TD * `COMP%`, data = WP)
NIM77	<-	lm(formula = ATT ~ TT * CAY * YDS * TD * INT * `COMP%`,  data = WP)
NIM78	<-	lm(formula = INT ~ `AGG%` * ATT * TD * `COMP%`, data = WP)
NIM79	<-	lm(formula = `COMP%` ~ TT * `AGG%` * AYTS * YDS *   TD * INT, data = WP)
NIM80	<-	lm(formula = TD ~ TT * CAY * `AGG%` * AYTS * YDS * INT *   `COMP%`, data = NGSP)
NIM81	<-	lm(formula = TT ~ `AGG%` * ATT * TD * `COMP%`, data = NGSP)
NIM82	<-	lm(formula = CAY ~ IAY * `COMP%`, data = NGSP)
NIM83	<-	lm(formula = IAY ~ CAY * LCAD * AYTS * ATT * `COMP%`, data = NGSP)
NIM84	<-	lm(formula = `AGG%` ~ TT * AYTS * ATT * INT * `COMP%`, data = NGSP)
NIM85	<-	lm(formula = LCAD ~ AYTS * YDS, data = NGSP)
NIM86	<-	lm(formula = AYTS ~ CAY * `AGG%` * LCAD * TD * `COMP%`,  data = NGSP)
NIM87	<-	lm(formula = ATT ~ TT * CAY * `AGG%` * YDS * `COMP%`,  data = NGSP)
NIM88	<-	lm(formula = INT ~ `AGG%` * ATT * TD, data = NGSP)
NIM89	<-	lm(formula = `COMP%` ~ TT * CAY * `AGG%` * AYTS *  YDS * TD, data = NGSP)
NIM90	<-	lm(formula = Yds ~ Rec * TD * FUM, data = WRW)
NIM91	<-	lm(formula = Avg ~ Rec * TD * FUM, data = WRW)
NIM92	<-	lm(formula = TD ~ Yds * FUM, data = WRW)
NIM93	<-	lm(formula = FUM ~ Rec * Avg * TD, data = WRW)
NIM94	<-	lm(formula = Rec ~ Yds * TD * FUM, data = WRW)
NIM95	<-	lm(formula = YDS ~ CUSH * SEP * TAY * REC * `CTCH%` * TD * `YAC/R`, data = ADVWRS)
NIM96	<-	lm(formula = CUSH ~ SEP * `CTCH%` * `YAC/R`, data = ADVWRS)
NIM97	<-	lm(formula = TAY ~ SEP * `CTCH%` * TD * `YAC/R`, data = ADVWRS)
NIM98	<-	lm(formula = SEP ~ CUSH * TAY * `CTCH%` * YDS * `YAC/R`, data = ADVWRS)
NIM99	<-	lm(formula = `TAY%` ~ CUSH * SEP * TAR * `CTCH%` * TD, data = ADVWRS)
NIM100	<-	lm(formula = REC ~ CUSH * SEP * TAY * `CTCH%` * YDS * `YAC/R`,  data = ADVWRS)
NIM101	<-	lm(formula = TAR ~ CUSH * SEP * TAY * `CTCH%` * YDS * `YAC/R`,  data = ADVWRS)
NIM102	<-	lm(formula = `CTCH%` ~ CUSH * SEP * TAY * YDS * TD * `YAC/R`,  data = ADVWRS)
NIM103	<-	lm(formula = TD ~ TAY * `CTCH%` * YDS, data = ADVWRS)
NIM104	<-	lm(formula = TD ~ Att * Yds, data = RUSHW)
NIM105	<-	lm(formula = Att ~ Yds * TD, data = RUSHW)
NIM106	<-	lm(formula = Yds ~ Att * TD, data = RUSHW)
NIM107	<-	lm(formula = Avg ~ Att * TD * FUM, data = RUSHW)
NIM108	<-	lm(formula = FUM ~ Att, data = RUSHW)
NIM109	<-	lm(formula = TD ~ YDS, data = ADVRUSHS)
NIM110	<-	lm(formula = EFF ~ `8+D%` * TLOS * TD, data = ADVRUSHS)
NIM111	<-	lm(formula = TLOS ~ EFF * `8+D%` * YDS, data = ADVRUSHS)
NIM112	<-	lm(formula = `8+D%` ~ EFF * TLOS, data = ADVRUSHS)
NIM113	<-	lm(formula = ATT ~ EFF * TLOS * YDS * TD, data = ADVRUSHS)
NIM114	<-	lm(formula = YDS ~ EFF * TLOS * ATT * TD, data = ADVRUSHS)
NIM115	<-	lm(formula = AVG ~ EFF * `8+D%` * TLOS * ATT * TD, data = ADVRUSHS)
NIM116	<-	lm(formula = Sacks ~ `QB Hits` * Tackles * Assists * `Fumbles Forced`, data = DEF_W)
NIM117	<-	lm(formula = `Sack Yds` ~ Sacks * Assists * `Fumbles Forced`, data = DEF_W)
NIM118	<-	lm(formula = `QB Hits` ~ Tackles * Assists * `Fumbles Forced`, data = DEF_W)
NIM119	<-	lm(formula = Tackles ~ Sacks * `QB Hits` * Assists * `Fumbles Forced`, data = DEF_W)
NIM120	<-	lm(formula = Assists ~ Sacks * `Sack Yds` * Tackles * `Fumbles Forced` * `Fumbles Recovered`, data = DEF_W)
NIM121	<-	lm(formula = `Fumbles Forced` ~ `Sack Yds` * Tackles *  Assists, data = DEF_W)
NIM122	<-	lm(formula = `Fumbles Recovered` ~ `Sack Yds` * Assists, data = DEF_W)
NIM123	<-	lm(formula = Int ~ Tgt * TD * DADOT * Bltz * Sk * Prss * TC * TM2, data = ADVDEF)
NIM124	<-	lm(formula = Tgt ~ Int * Yds * TD * DADOT * Bltz * Sk * TC, data = ADVDEF)
NIM125	<-	lm(formula = Cmp ~ Yds * TD * DADOT * YAC * Bltz * QBKD * Sk * TC, data = ADVDEF)
NIM126	<-	lm(formula = Yds ~ Int * Cmp * TD * DADOT * Bltz * Sk * Prss * TC, data = ADVDEF)
NIM127	<-	lm(formula = TD ~ Int * Yds * DADOT * YAC * TM2, data = ADVDEF)
NIM128	<-	lm(formula = DADOT ~ Int * Yds * TD * YAC * Bltz * Sk * TC, data = ADVDEF)
NIM129	<-	lm(formula = Air ~ Tgt * TD * DADOT * YAC * Bltz * Sk * TC, data = ADVDEF)
NIM130	<-	lm(formula = YAC ~ Int * Cmp * TD * DADOT * Bltz * Hrry * QBKD * TC * TM2, data = ADVDEF)
NIM131	<-	lm(formula = Bltz ~ Tgt * TD * DADOT * YAC * Sk * TC * TM2, data = ADVDEF)
NIM132	<-	lm(formula = Hrry ~ Int * DADOT * YAC * Bltz * Sk * TC * TM2, data = ADVDEF)
NIM133	<-	lm(formula = QBKD ~ Prss * TC, data = ADVDEF)
NIM134	<-	lm(formula = Sk ~ Yds * DADOT * YAC * Bltz * TC, data = ADVDEF)
NIM135	<-	lm(formula = Prss ~ Int * DADOT * YAC * Sk * TC * TM2, data = ADVDEF)
NIM136	<-	lm(formula = TC ~ Int * Cmp * DADOT * YAC * Bltz * Sk * TM2, data = ADVDEF)
NIM137	<-	lm(formula = TM2 ~ Int * TD * YAC * Bltz * TC, data = ADVDEF)
NIM138	<-	lm(formula = TD ~ AYTS * ATT * YDS * INT * `COMP%` * Week, data = Weekly_Passing)
NIM139	<-	lm(formula = TT ~ CAY * IAY * `AGG%` * LCAD * ATT * `COMP%` * Week, data = Weekly_Passing)
NIM140	<-	lm(formula = CAY ~ IAY * AYD * LCAD * AYTS * YDS * Week, data = Weekly_Passing)
NIM141	<-	lm(formula = IAY ~ CAY * AYD * YDS * Week, data = Weekly_Passing)
NIM142	<-	lm(formula = AYD ~ CAY * IAY * AYTS * YDS * Week, data = Weekly_Passing)
NIM143	<-	lm(formula = `AGG%` ~ TT * IAY * YDS * `COMP%` * Week, data = Weekly_Passing)
NIM144	<-	lm(formula = LCAD ~ TT * CAY * YDS * TD * Week, data = Weekly_Passing)
NIM145	<-	lm(formula = AYTS ~ IAY * YDS * TD * Week, data = Weekly_Passing)
NIM146	<-	lm(formula = ATT ~ TT * IAY * AYD * YDS * TD * INT * `COMP%` *  Week, data = Weekly_Passing)
NIM147	<-	lm(formula = INT ~ AYD * `AGG%` * ATT * TD * `COMP%`, data = Weekly_Passing)
NIM148	<-	lm(formula = `COMP%` ~ TT * IAY * AYD * `AGG%` * ATT * YDS * TD * INT, data = Weekly_Passing)
NIM149	<-	lm(formula = TD ~ TT * CAY * `AGG%` * AYTS * YDS * INT *  `COMP%`, data = NEXT_GEN_STATS_PASSING)
NIM150	<-	lm(formula = TT ~ `AGG%` * YDS * TD * `COMP%`, data = NEXT_GEN_STATS_PASSING)
NIM151	<-	lm(formula = CAY ~ TT * IAY * AYD, data = NEXT_GEN_STATS_PASSING)
NIM152	<-	lm(formula = IAY ~ `AGG%` * LCAD * AYTS * `COMP%`, data = NEXT_GEN_STATS_PASSING)
NIM153	<-	lm(formula = AYD ~ TT * CAY * IAY, data = NEXT_GEN_STATS_PASSING)
NIM154	<-	lm(formula = `AGG%` ~ IAY * YDS * INT, data = NEXT_GEN_STATS_PASSING)
NIM155	<-	lm(formula = LCAD ~ IAY * YDS, data = NEXT_GEN_STATS_PASSING)
NIM156	<-	lm(formula = AYTS ~ IAY * TD, data = NEXT_GEN_STATS_PASSING)
NIM157	<-	lm(formula = ATT ~ TT * CAY * `AGG%` * YDS * `COMP%`, data = NEXT_GEN_STATS_PASSING)
NIM158	<-	lm(formula = INT ~ `AGG%` * ATT * TD, data = NEXT_GEN_STATS_PASSING)
NIM159	<-	lm(formula = `COMP%` ~ TT * AYD * `AGG%` * YDS * TD, data = NEXT_GEN_STATS_PASSING)
NIM160	<-	lm(formula = Yds ~ Rec * Avg * TD * FUM, data = REC_WEEKLY)
NIM161	<-	lm(formula = Avg ~ Rec * Yds * TD, data = REC_WEEKLY)
NIM162	<-	lm(formula = TD ~ Rec * Yds * Avg * FUM, data = REC_WEEKLY)
NIM163	<-	lm(formula = FUM ~ Rec * Yds * TD, data = REC_WEEKLY)
NIM164	<-	lm(formula = Rec ~ Yds * Avg * TD * FUM, data = REC_WEEKLY)
NIM165	<-	lm(formula = YDS ~ CUSH * SEP * TAY * TAR * `CTCH%` * `YAC/R`,    data = Next_gen_stats_receving)
NIM166	<-	lm(formula = CUSH ~ SEP * `TAY%` * `CTCH%` * YDS *  `YAC/R`, data = Next_gen_stats_receving)
NIM167	<-	lm(formula = TAY ~ SEP * `TAY%` * TAR * `CTCH%` * TD * `YAC/R`, data = Next_gen_stats_receving)
NIM168	<-	lm(formula = SEP ~ CUSH * TAY * `CTCH%` * YDS * `YAC/R` *  `xYAC/R`, data = Next_gen_stats_receving)
NIM169	<-	lm(formula = `TAY%` ~ CUSH * TAY * `CTCH%` * YDS *  `YAC/R` * `xYAC/R`, data = Next_gen_stats_receving)
NIM170	<-	lm(formula = REC ~ TAR * `CTCH%` * `xYAC/R`, data = Next_gen_stats_receving)
NIM171	<-	lm(formula = TAR ~ TAY * `TAY%` * REC * `CTCH%` * TD, data = Next_gen_stats_receving)
NIM172	<-	lm(formula = `CTCH%` ~ CUSH * SEP * TAY * `TAY%` * REC * TD * `YAC/R`, data = Next_gen_stats_receving)
NIM173	<-	lm(formula = TD ~ TAY * `CTCH%` * YDS * `YAC/R` *  `xYAC/R`, data = Next_gen_stats_receving)
NIM174	<-	lm(formula = TD ~ Att * Yds, data = Weekly_Rushing_Stats)
NIM175	<-	lm(formula = Att ~ Yds * Avg * TD, data = Weekly_Rushing_Stats)
NIM176	<-	lm(formula = Yds ~ Att * Avg * TD * FUM, data = Weekly_Rushing_Stats)
NIM177	<-	lm(formula = Avg ~ Att * Yds * FUM, data = Weekly_Rushing_Stats)
NIM178	<-	lm(formula = FUM ~ Yds * Avg, data = Weekly_Rushing_Stats)
NIM179	<-	lm(formula = TD ~ YDS, data = NGSR)
NIM180	<-	lm(formula = EFF ~ `8+D%` * TLOS * YDS * AVG * TD, data = NGSR)
NIM181	<-	lm(formula = TLOS ~ EFF * `8+D%` * AVG, data = NGSR)
NIM182	<-	lm(formula = `8+D%` ~ EFF * TLOS * AVG, data = NGSR)
NIM183	<-	lm(formula = ATT ~ EFF * YDS * AVG * TD, data = NGSR)
NIM184	<-	lm(formula = YDS ~ EFF * ATT * AVG * TD, data = NGSR)
NIM185	<-	lm(formula = AVG ~ EFF * `8+D%` * TLOS * TD, data = NGSR)
NIM186	<-	lm(formula = Sacks ~ `Sack Yds` * `QB Hits` * Tackles *  Assists * `Fumbles Forced`, data = Defense_Weekly)
NIM187	<-	lm(formula = `Sack Yds` ~ Sacks * `QB Hits` * Assists *  `Fumbles Forced`, data = Defense_Weekly)
NIM188	<-	lm(formula = `QB Hits` ~ Sacks * `Sack Yds` * Tackles *  Assists * `Fumbles Forced`, data = Defense_Weekly)
NIM189	<-	lm(formula = Tackles ~ Sacks * `QB Hits` * Assists * `Fumbles Forced`, data = Defense_Weekly)
NIM190	<-	lm(formula = Assists ~ Sacks * `Sack Yds` * `QB Hits` * Tackles * `Fumbles Forced` * `Fumbles Recovered`, data = Defense_Weekly)
NIM191	<-	lm(formula = `Fumbles Forced` ~ Sacks * `Sack Yds` *  `QB Hits` * Tackles * Assists * `Fumbles Recovered`, data = Defense_Weekly)
NIM192	<-	lm(formula = `Fumbles Recovered` ~ Assists * `Fumbles Forced`, data = Defense_Weekly)
NIM193	<-	lm(formula = Int ~ Tgt * TD * DADOT * Bltz * TC * TM2, data = MODADV)
NIM194	<-	lm(formula = Tgt ~ Int * Yds * TD * DADOT * Bltz * QBKD * Prss *  TC * TM2, data = MODADV)
NIM195	<-	lm(formula = Cmp ~ Int * Tgt * TD * DADOT * YAC * Bltz * Prss * TC * TM2, data = MODADV)
NIM196	<-	lm(formula = Yds ~ Air * YAC, data = MODADV)
NIM197	<-	lm(formula = TD ~ Int * Yds * DADOT * YAC * TM2, data = MODADV)
NIM198	<-	lm(formula = DADOT ~ Int * Yds * TD * YAC * Bltz * Sk * Prss * TC, data = MODADV)
NIM199	<-	lm(formula = Air ~ Yds * YAC, data = MODADV)
NIM200	<-	lm(formula = YAC ~ Int * Cmp * TD * DADOT * Bltz * Hrry * QBKD *  TC * TM2, data = MODADV)
NIM201	<-	lm(formula = Bltz ~ Int * Cmp * TD * DADOT * YAC * QBKD * Sk *  TC * TM2, data = MODADV)
NIM202	<-	lm(formula = Hrry ~ DADOT * YAC * Bltz * QBKD * Sk * TC * TM2, data = MODADV)
NIM203	<-	lm(formula = QBKD ~ Bltz * Sk * Prss * TM2, data = MODADV)
NIM204	<-	lm(formula = Sk ~ Int * Bltz * QBKD * Prss * TM2, data = MODADV)
NIM205	<-	lm(formula = Prss ~ Int * TD * Bltz * Hrry * QBKD * Sk * TC,  data = MODADV)
NIM206	<-	lm(formula = TC ~ Int * Cmp * DADOT * YAC * Bltz * Prss * TM2,  data = MODADV)
NIM207	<-	lm(formula = TM2 ~ Int * TD * YAC * Bltz * Sk * Prss * TC, data = MODADV)
NIM208	<-	lm(formula = TD ~ CAY * AYTS * YDS * INT * `COMP%` * Week,  data = Weekly_Passing)
NIM209	<-	lm(formula = TT ~ IAY * `AGG%` * LCAD * ATT * TD * `COMP%` *  Week, data = Weekly_Passing)
NIM210	<-	lm(formula = CAY ~ TT * IAY * LCAD * AYTS * TD * INT * `COMP%`, data = Weekly_Passing)
NIM211	<-	lm(formula = IAY ~ TT * CAY * `AGG%` * AYTS * TD * INT * `COMP%` * Week, data = Weekly_Passing)
NIM212	<-	lm(formula = `AGG%` ~ TT * AYTS * ATT * INT * `COMP%` *  Week, data = Weekly_Passing)
NIM213	<-	lm(formula = LCAD ~ TT * CAY * YDS * TD * Week, data = Weekly_Passing)
NIM214	<-	lm(formula = AYTS ~ TT * CAY * `AGG%` * TD * `COMP%`,   data = Weekly_Passing)
NIM215	<-	lm(formula = ATT ~ TT * CAY * YDS * TD * INT * `COMP%` * Week, data = Weekly_Passing)
NIM216	<-	lm(formula = INT ~ `AGG%` * ATT * TD * `COMP%`, data = Weekly_Passing)
NIM217	<-	lm(formula = `COMP%` ~ TT * `AGG%` * AYTS * YDS *  TD * INT, data = Weekly_Passing)
NIM218	<-	lm(formula = TD ~ TT * CAY * `AGG%` * AYTS * YDS * INT * `COMP%`, data = NEXT_GEN_STATS_PASSING)
NIM219	<-	lm(formula = TT ~ `AGG%` * ATT * TD * `COMP%`, data = NEXT_GEN_STATS_PASSING)
NIM220	<-	lm(formula = CAY ~ IAY * `COMP%`, data = NEXT_GEN_STATS_PASSING)
NIM221	<-	lm(formula = IAY ~ CAY * LCAD * AYTS * ATT * `COMP%`, data = NEXT_GEN_STATS_PASSING)
NIM222	<-	lm(formula = `AGG%` ~ TT * AYTS * ATT * INT * `COMP%`, data = NEXT_GEN_STATS_PASSING)
NIM223	<-	lm(formula = LCAD ~ AYTS * YDS, data = NEXT_GEN_STATS_PASSING)
NIM224	<-	lm(formula = AYTS ~ CAY * `AGG%` * LCAD * TD * `COMP%`,  data = NEXT_GEN_STATS_PASSING)
NIM225	<-	lm(formula = ATT ~ TT * CAY * `AGG%` * YDS * `COMP%`, data = NEXT_GEN_STATS_PASSING)
NIM226	<-	lm(formula = INT ~ `AGG%` * ATT * TD, data = NEXT_GEN_STATS_PASSING)
NIM227	<-	lm(formula = `COMP%` ~ TT * CAY * `AGG%` * AYTS * YDS * TD, data = NEXT_GEN_STATS_PASSING)
NIM228	<-	lm(formula = Yds ~ Rec * TD * FUM, data = REC_WEEKLY)
NIM229	<-	lm(formula = Avg ~ Rec * TD * FUM, data = REC_WEEKLY)
NIM230	<-	lm(formula = TD ~ Yds * FUM, data = REC_WEEKLY)
NIM231	<-	lm(formula = FUM ~ Rec * Avg * TD, data = REC_WEEKLY)
NIM232	<-	lm(formula = Rec ~ Yds * TD * FUM, data = REC_WEEKLY)
NIM233	<-	lm(formula = YDS ~ CUSH * SEP * TAY * REC * `CTCH%` * TD * `YAC/R`, data = Next_gen_stats_receving)
NIM234	<-	lm(formula = CUSH ~ SEP * `CTCH%` * `YAC/R`, data = Next_gen_stats_receving)
NIM235	<-	lm(formula = TAY ~ SEP * `CTCH%` * TD * `YAC/R`,  data = Next_gen_stats_receving)
NIM236	<-	lm(formula = SEP ~ CUSH * TAY * `CTCH%` * YDS * `YAC/R`, data = Next_gen_stats_receving)
NIM237	<-	lm(formula = `TAY%` ~ CUSH * SEP * TAR * `CTCH%` *  TD, data = Next_gen_stats_receving)
NIM238	<-	lm(formula = REC ~ CUSH * SEP * TAY * `CTCH%` * YDS * `YAC/R`,  data = Next_gen_stats_receving)
NIM239	<-	lm(formula = TAR ~ CUSH * SEP * TAY * `CTCH%` * YDS * `YAC/R`,  data = Next_gen_stats_receving)
NIM240	<-	lm(formula = `CTCH%` ~ CUSH * SEP * TAY * YDS * TD * `YAC/R`,  data = Next_gen_stats_receving)
NIM241	<-	lm(formula = TD ~ TAY * `CTCH%` * YDS, data = Next_gen_stats_receving)
NIM242	<-	lm(formula = TD ~ Att * Yds, data = Weekly_Rushing_Stats)
NIM243	<-	lm(formula = Att ~ Yds * TD, data = Weekly_Rushing_Stats)
NIM244	<-	lm(formula = Yds ~ Att * TD, data = Weekly_Rushing_Stats)
NIM245	<-	lm(formula = Avg ~ Att * TD * FUM, data = Weekly_Rushing_Stats)
NIM246	<-	lm(formula = FUM ~ Att, data = Weekly_Rushing_Stats)
NIM247	<-	lm(formula = TD ~ YDS, data = NGSR)
NIM248	<-	lm(formula = EFF ~ `8+D%` * TLOS * TD, data = NGSR)
NIM249	<-	lm(formula = TLOS ~ EFF * `8+D%` * YDS, data = NGSR)
NIM250	<-	lm(formula = `8+D%` ~ EFF * TLOS, data = NGSR)
NIM251	<-	lm(formula = ATT ~ EFF * TLOS * YDS * TD, data = NGSR)
NIM252	<-	lm(formula = YDS ~ EFF * TLOS * ATT * TD, data = NGSR)
NIM253	<-	lm(formula = AVG ~ EFF * `8+D%` * TLOS * ATT * TD, data = NGSR)
NIM254	<-	lm(formula = Sacks ~ `QB Hits` * Tackles * Assists * `Fumbles Forced`,  data = Defense_Weekly)
NIM255	<-	lm(formula = `Sack Yds` ~ Sacks * Assists * `Fumbles Forced`,  data = Defense_Weekly)
NIM256	<-	lm(formula = `QB Hits` ~ Tackles * Assists * `Fumbles Forced`,  data = Defense_Weekly)
NIM257	<-	lm(formula = Tackles ~ Sacks * `Sack Yds` * `QB Hits` * Assists * `Fumbles Forced`, data = Defense_Weekly)
NIM258	<-	lm(formula = Assists ~ Sacks * `Sack Yds` * Tackles * `Fumbles Forced`,  data = Defense_Weekly)
NIM259	<-	lm(formula = `Fumbles Forced` ~ `Sack Yds` * Tackles *  Assists, data = Defense_Weekly)
NIM260	<-	lm(formula = `Fumbles Recovered` ~ `Sack Yds` * Assists,  data = Defense_Weekly)
NIM261	<-	lm(formula = Int ~ Tgt * TD * DADOT * Bltz * Sk * Prss * TC *  TM2, data = MODADV)
NIM262	<-	lm(formula = Tgt ~ Int * Yds * TD * DADOT * Bltz * Sk * TC, data = MODADV)
NIM263	<-	lm(formula = Cmp ~ Yds * TD * DADOT * YAC * Bltz * QBKD * Sk * TC, data = MODADV)
NIM264	<-	lm(formula = Yds ~ Int * Cmp * TD * DADOT * Bltz * Sk * Prss *  TC, data = MODADV)
NIM265	<-	lm(formula = TD ~ Int * Yds * DADOT * YAC * TM2, data = MODADV)
NIM266	<-	lm(formula = DADOT ~ Int * Yds * TD * YAC * Bltz * Sk * TC, data = MODADV)
NIM267	<-	lm(formula = Air ~ Tgt * TD * DADOT * YAC * Bltz * Sk * TC, data = MODADV)
NIM268	<-	lm(formula = YAC ~ Int * Cmp * TD * DADOT * Bltz * Hrry * QBKD *  TC * TM2, data = MODADV)
NIM269	<-	lm(formula = Bltz ~ Tgt * TD * DADOT * YAC * Sk * TC * TM2, data = MODADV)
NIM270	<-	lm(formula = Hrry ~ Int * DADOT * YAC * Bltz * Sk * TC * TM2,  data = MODADV)
NIM271	<-	lm(formula = QBKD ~ Prss * TC, data = MODADV)
NIM272	<-	lm(formula = Sk ~ Yds * DADOT * YAC * Bltz * TC, data = MODADV)
NIM273	<-	lm(formula = Prss ~ Int * DADOT * YAC * Sk * TC * TM2, data = MODADV)
NIM274	<-	lm(formula = TC ~ Int * Cmp * DADOT * YAC * Bltz * Sk * TM2, data = MODADV)
NIM275	<-	lm(formula = TM2 ~ Int * TD * YAC * Bltz * TC, data = MODADV)

```



```{r}
# Step interaction models 

ST_NIM1	<-	step(	NIM1	)
ST_NIM2	<-	step(	NIM2	)
ST_NIM3	<-	step(	NIM3	)
ST_NIM4	<-	step(	NIM4	)
ST_NIM5	<-	step(	NIM5	)
ST_NIM6	<-	step(	NIM6	)
ST_NIM7	<-	step(	NIM7	)
ST_NIM8	<-	step(	NIM8	)
ST_NIM9	<-	step(	NIM9	)
ST_NIM10	<-	step(	NIM10	)
ST_NIM11	<-	step(	NIM11	)
ST_NIM12	<-	step(	NIM12	)
ST_NIM13	<-	step(	NIM13	)
ST_NIM14	<-	step(	NIM14	)
ST_NIM15	<-	step(	NIM15	)
ST_NIM16	<-	step(	NIM16	)
ST_NIM17	<-	step(	NIM17	)
ST_NIM18	<-	step(	NIM18	)
ST_NIM19	<-	step(	NIM19	)
ST_NIM20	<-	step(	NIM20	)
ST_NIM21	<-	step(	NIM21	)
ST_NIM22	<-	step(	NIM22	)
ST_NIM23	<-	step(	NIM23	)
ST_NIM24	<-	step(	NIM24	)
ST_NIM25	<-	step(	NIM25	)
ST_NIM26	<-	step(	NIM26	)
ST_NIM27	<-	step(	NIM27	)
ST_NIM28	<-	step(	NIM28	)
ST_NIM29	<-	step(	NIM29	)
ST_NIM30	<-	step(	NIM30	)
ST_NIM31	<-	step(	NIM31	)
ST_NIM32	<-	step(	NIM32	)
ST_NIM33	<-	step(	NIM33	)
ST_NIM34	<-	step(	NIM34	)
ST_NIM35	<-	step(	NIM35	)
ST_NIM36	<-	step(	NIM36	)
ST_NIM37	<-	step(	NIM37	)
ST_NIM38	<-	step(	NIM38	)
ST_NIM39	<-	step(	NIM39	)
ST_NIM40	<-	step(	NIM40	)
ST_NIM41	<-	step(	NIM41	)
ST_NIM42	<-	step(	NIM42	)
ST_NIM43	<-	step(	NIM43	)
ST_NIM44	<-	step(	NIM44	)
ST_NIM45	<-	step(	NIM45	)
ST_NIM46	<-	step(	NIM46	)
ST_NIM47	<-	step(	NIM47	)
ST_NIM48	<-	step(	NIM48	)
ST_NIM49	<-	step(	NIM49	)
ST_NIM50	<-	step(	NIM50	)
ST_NIM51	<-	step(	NIM51	)
ST_NIM52	<-	step(	NIM52	)
ST_NIM53	<-	step(	NIM53	)
ST_NIM54	<-	step(	NIM54	)
ST_NIM55	<-	step(	NIM55	)
ST_NIM56	<-	step(	NIM56	)
ST_NIM57	<-	step(	NIM57	)
ST_NIM58	<-	step(	NIM58	)
ST_NIM59	<-	step(	NIM59	)
ST_NIM60	<-	step(	NIM60	)
ST_NIM61	<-	step(	NIM61	)
ST_NIM62	<-	step(	NIM62	)
ST_NIM63	<-	step(	NIM63	)
ST_NIM64	<-	step(	NIM64	)
ST_NIM65	<-	step(	NIM65	)
ST_NIM66	<-	step(	NIM66	)
ST_NIM67	<-	step(	NIM67	)
ST_NIM68	<-	step(	NIM68	)
ST_NIM69	<-	step(	NIM69	)
ST_NIM70	<-	step(	NIM70	)
ST_NIM71	<-	step(	NIM71	)
ST_NIM72	<-	step(	NIM72	)
ST_NIM73	<-	step(	NIM73	)
ST_NIM74	<-	step(	NIM74	)
ST_NIM75	<-	step(	NIM75	)
ST_NIM76	<-	step(	NIM76	)
ST_NIM77	<-	step(	NIM77	)
ST_NIM78	<-	step(	NIM78	)
ST_NIM79	<-	step(	NIM79	)
ST_NIM80	<-	step(	NIM80	)
ST_NIM81	<-	step(	NIM81	)
ST_NIM82	<-	step(	NIM82	)
ST_NIM83	<-	step(	NIM83	)
ST_NIM84	<-	step(	NIM84	)
ST_NIM85	<-	step(	NIM85	)
ST_NIM86	<-	step(	NIM86	)
ST_NIM87	<-	step(	NIM87	)
ST_NIM88	<-	step(	NIM88	)
ST_NIM89	<-	step(	NIM89	)
ST_NIM90	<-	step(	NIM90	)
ST_NIM91	<-	step(	NIM91	)
ST_NIM92	<-	step(	NIM92	)
ST_NIM93	<-	step(	NIM93	)
ST_NIM94	<-	step(	NIM94	)
ST_NIM95	<-	step(	NIM95	)
ST_NIM96	<-	step(	NIM96	)
ST_NIM97	<-	step(	NIM97	)
ST_NIM98	<-	step(	NIM98	)
ST_NIM99	<-	step(	NIM99	)
ST_NIM100	<-	step(	NIM100	)
ST_NIM101	<-	step(	NIM101	)
ST_NIM102	<-	step(	NIM102	)
ST_NIM103	<-	step(	NIM103	)
ST_NIM104	<-	step(	NIM104	)
ST_NIM105	<-	step(	NIM105	)
ST_NIM106	<-	step(	NIM106	)
ST_NIM107	<-	step(	NIM107	)
ST_NIM108	<-	step(	NIM108	)
ST_NIM109	<-	step(	NIM109	)
ST_NIM110	<-	step(	NIM110	)
ST_NIM111	<-	step(	NIM111	)
ST_NIM112	<-	step(	NIM112	)
ST_NIM113	<-	step(	NIM113	)
ST_NIM114	<-	step(	NIM114	)
ST_NIM115	<-	step(	NIM115	)
ST_NIM116	<-	step(	NIM116	)
ST_NIM117	<-	step(	NIM117	)
ST_NIM118	<-	step(	NIM118	)
ST_NIM119	<-	step(	NIM119	)
ST_NIM120	<-	step(	NIM120	)
ST_NIM121	<-	step(	NIM121	)
ST_NIM122	<-	step(	NIM122	)
ST_NIM123	<-	step(	NIM123	)
ST_NIM124	<-	step(	NIM124	)
ST_NIM125	<-	step(	NIM125	)
ST_NIM126	<-	step(	NIM126	)
ST_NIM127	<-	step(	NIM127	)
ST_NIM128	<-	step(	NIM128	)
ST_NIM129	<-	step(	NIM129	)
ST_NIM130	<-	step(	NIM130	)
ST_NIM131	<-	step(	NIM131	)
ST_NIM132	<-	step(	NIM132	)
ST_NIM133	<-	step(	NIM133	)
ST_NIM134	<-	step(	NIM134	)
ST_NIM135	<-	step(	NIM135	)
ST_NIM136	<-	step(	NIM136	)
ST_NIM137	<-	step(	NIM137	)
ST_NIM138	<-	step(	NIM138	)
ST_NIM139	<-	step(	NIM139	)
ST_NIM140	<-	step(	NIM140	)
ST_NIM141	<-	step(	NIM141	)
ST_NIM142	<-	step(	NIM142	)
ST_NIM143	<-	step(	NIM143	)
ST_NIM144	<-	step(	NIM144	)
ST_NIM145	<-	step(	NIM145	)
ST_NIM146	<-	step(	NIM146	)
ST_NIM147	<-	step(	NIM147	)
ST_NIM148	<-	step(	NIM148	)
ST_NIM149	<-	step(	NIM149	)
ST_NIM150	<-	step(	NIM150	)
ST_NIM151	<-	step(	NIM151	)
ST_NIM152	<-	step(	NIM152	)
ST_NIM153	<-	step(	NIM153	)
ST_NIM154	<-	step(	NIM154	)
ST_NIM155	<-	step(	NIM155	)
ST_NIM156	<-	step(	NIM156	)
ST_NIM157	<-	step(	NIM157	)
ST_NIM158	<-	step(	NIM158	)
ST_NIM159	<-	step(	NIM159	)
ST_NIM160	<-	step(	NIM160	)
ST_NIM161	<-	step(	NIM161	)
ST_NIM162	<-	step(	NIM162	)
ST_NIM163	<-	step(	NIM163	)
ST_NIM164	<-	step(	NIM164	)
ST_NIM165	<-	step(	NIM165	)
ST_NIM166	<-	step(	NIM166	)
ST_NIM167	<-	step(	NIM167	)
ST_NIM168	<-	step(	NIM168	)
ST_NIM169	<-	step(	NIM169	)
ST_NIM170	<-	step(	NIM170	)
ST_NIM171	<-	step(	NIM171	)
ST_NIM172	<-	step(	NIM172	)
ST_NIM173	<-	step(	NIM173	)
ST_NIM174	<-	step(	NIM174	)
ST_NIM175	<-	step(	NIM175	)
ST_NIM176	<-	step(	NIM176	)
ST_NIM177	<-	step(	NIM177	)
ST_NIM178	<-	step(	NIM178	)
ST_NIM179	<-	step(	NIM179	)
ST_NIM180	<-	step(	NIM180	)
ST_NIM181	<-	step(	NIM181	)
ST_NIM182	<-	step(	NIM182	)
ST_NIM183	<-	step(	NIM183	)
ST_NIM184	<-	step(	NIM184	)
ST_NIM185	<-	step(	NIM185	)
ST_NIM186	<-	step(	NIM186	)
ST_NIM187	<-	step(	NIM187	)
ST_NIM188	<-	step(	NIM188	)
ST_NIM189	<-	step(	NIM189	)
ST_NIM190	<-	step(	NIM190	)
ST_NIM191	<-	step(	NIM191	)
ST_NIM192	<-	step(	NIM192	)
ST_NIM193	<-	step(	NIM193	)
ST_NIM194	<-	step(	NIM194	)
ST_NIM195	<-	step(	NIM195	)
ST_NIM196	<-	step(	NIM196	)
ST_NIM197	<-	step(	NIM197	)
ST_NIM198	<-	step(	NIM198	)
ST_NIM199	<-	step(	NIM199	)
ST_NIM200	<-	step(	NIM200	)
ST_NIM201	<-	step(	NIM201	)
ST_NIM202	<-	step(	NIM202	)
ST_NIM203	<-	step(	NIM203	)
ST_NIM204	<-	step(	NIM204	)
ST_NIM205	<-	step(	NIM205	)
ST_NIM206	<-	step(	NIM206	)
ST_NIM207	<-	step(	NIM207	)
ST_NIM208	<-	step(	NIM208	)
ST_NIM209	<-	step(	NIM209	)
ST_NIM210	<-	step(	NIM210	)
ST_NIM211	<-	step(	NIM211	)
ST_NIM212	<-	step(	NIM212	)
ST_NIM213	<-	step(	NIM213	)
ST_NIM214	<-	step(	NIM214	)
ST_NIM215	<-	step(	NIM215	)
ST_NIM216	<-	step(	NIM216	)
ST_NIM217	<-	step(	NIM217	)
ST_NIM218	<-	step(	NIM218	)
ST_NIM219	<-	step(	NIM219	)
ST_NIM220	<-	step(	NIM220	)
ST_NIM221	<-	step(	NIM221	)
ST_NIM222	<-	step(	NIM222	)
ST_NIM223	<-	step(	NIM223	)
ST_NIM224	<-	step(	NIM224	)
ST_NIM225	<-	step(	NIM225	)
ST_NIM226	<-	step(	NIM226	)
ST_NIM227	<-	step(	NIM227	)
ST_NIM228	<-	step(	NIM228	)
ST_NIM229	<-	step(	NIM229	)
ST_NIM230	<-	step(	NIM230	)
ST_NIM231	<-	step(	NIM231	)
ST_NIM232	<-	step(	NIM232	)
ST_NIM233	<-	step(	NIM233	)
ST_NIM234	<-	step(	NIM234	)
ST_NIM235	<-	step(	NIM235	)
ST_NIM236	<-	step(	NIM236	)
ST_NIM237	<-	step(	NIM237	)
ST_NIM238	<-	step(	NIM238	)
ST_NIM239	<-	step(	NIM239	)
ST_NIM240	<-	step(	NIM240	)
ST_NIM241	<-	step(	NIM241	)
ST_NIM242	<-	step(	NIM242	)
ST_NIM243	<-	step(	NIM243	)
ST_NIM244	<-	step(	NIM244	)
ST_NIM245	<-	step(	NIM245	)
ST_NIM246	<-	step(	NIM246	)
ST_NIM247	<-	step(	NIM247	)
ST_NIM248	<-	step(	NIM248	)
ST_NIM249	<-	step(	NIM249	)
ST_NIM250	<-	step(	NIM250	)
ST_NIM251	<-	step(	NIM251	)
ST_NIM252	<-	step(	NIM252	)
ST_NIM253	<-	step(	NIM253	)
ST_NIM254	<-	step(	NIM254	)
ST_NIM255	<-	step(	NIM255	)
ST_NIM256	<-	step(	NIM256	)
ST_NIM257	<-	step(	NIM257	)
ST_NIM258	<-	step(	NIM258	)
ST_NIM259	<-	step(	NIM259	)
ST_NIM260	<-	step(	NIM260	)
ST_NIM261	<-	step(	NIM261	)
ST_NIM262	<-	step(	NIM262	)
ST_NIM263	<-	step(	NIM263	)
ST_NIM264	<-	step(	NIM264	)
ST_NIM265	<-	step(	NIM265	)
ST_NIM266	<-	step(	NIM266	)
ST_NIM267	<-	step(	NIM267	)
ST_NIM268	<-	step(	NIM268	)
ST_NIM269	<-	step(	NIM269	)
ST_NIM270	<-	step(	NIM270	)
ST_NIM271	<-	step(	NIM271	)
ST_NIM272	<-	step(	NIM272	)
ST_NIM273	<-	step(	NIM273	)
ST_NIM274	<-	step(	NIM274	)
ST_NIM275	<-	step(	NIM275	)

```


```{r}
tree_func <- function(final_model, 
                      tree_num) {
  
  # get tree by index
  tree <- randomForest::getTree(final_model, 
                                k = tree_num, 
                                labelVar = TRUE) %>%
    tibble::rownames_to_column() %>%
    # make leaf split points to NA, so the 0s won't get plotted
    mutate(`split point` = ifelse(is.na(prediction), `split point`, NA))
  
  # prepare data frame for graph
  graph_frame <- data.frame(from = rep(tree$rowname, 2),
                            to = c(tree$`left daughter`, tree$`right daughter`))
  
  # convert to graph and delete the last node that we don't want to plot
  graph <- graph_from_data_frame(graph_frame) %>%
    delete_vertices("0")
  
  # set node labels
  V(graph)$node_label <- gsub("_", " ", as.character(tree$`split var`))
  V(graph)$leaf_label <- as.character(tree$prediction)
  V(graph)$split <- as.character(round(tree$`split point`, digits = 2))
  
  # plot
  plot <- ggraph::ggraph(graph, 'dendrogram') + 
    theme_bw() +
    ggraph::geom_edge_link() +
    geom_node_point() +
    geom_node_text(aes(label = node_label), na.rm = TRUE, repel = TRUE) +
    geom_node_label(aes(label = split), vjust = 2.5, na.rm = TRUE, fill = "white") +
    geom_node_label(aes(label = leaf_label, fill = leaf_label), na.rm = TRUE, 
					repel = TRUE, colour = "white", fontface = "bold", show.legend = FALSE) +
    theme(panel.grid.minor = element_blank(),
          panel.grid.major = element_blank(),
          panel.background = element_blank(),
          plot.background = element_rect(fill = "white"),
          panel.border = element_blank(),
          axis.line = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          plot.title = element_text(size = 8))
  
  print(plot)
}

```


```{r}
library(dplyr)
library(ggraph)
library(igraph)

tree_func <- function(final_model, 
                      tree_num) {
  
  # get tree by index
  tree <- randomForest::getTree(final_model, 
                                k = tree_num, 
                                labelVar = TRUE) %>%
    tibble::rownames_to_column() %>%
    # make leaf split points to NA, so the 0s won't get plotted
    mutate(`split point` = ifelse(is.na(prediction), `split point`, NA))
  
  # prepare data frame for graph
  graph_frame <- data.frame(from = rep(tree$rowname, 2),
                            to = c(tree$`left daughter`, tree$`right daughter`))
  
  # convert to graph and delete the last node that we don't want to plot
  graph <- graph_from_data_frame(graph_frame) %>%
    delete_vertices("0")
  
  # set node labels
  V(graph)$node_label <- gsub("_", " ", as.character(tree$`split var`))
  V(graph)$leaf_label <- as.character(tree$prediction)
  V(graph)$split <- as.character(round(tree$`split point`, digits = 2))
  
  # plot
  plot <- ggraph(graph, 'dendrogram') + 
    theme_bw() +
    geom_edge_link() +
    geom_node_point() +
    geom_node_text(aes(label = node_label), na.rm = TRUE, repel = TRUE) +
    geom_node_label(aes(label = split), vjust = 2.5, na.rm = TRUE, fill = "white") +
    geom_node_label(aes(label = leaf_label, fill = leaf_label), na.rm = TRUE, 
					repel = TRUE, colour = "white", fontface = "bold", show.legend = FALSE) +
    theme(panel.grid.minor = element_blank(),
          panel.grid.major = element_blank(),
          panel.background = element_blank(),
          plot.background = element_rect(fill = "white"),
          panel.border = element_blank(),
          axis.line = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          plot.title = element_text(size = 18))
  
  print(plot)
}
```




```{r}
#Weekly passing Touchdowns
sample_wp_td <- sample.split(Weekly_Passing$td,SplitRatio = 0.75)
train_wp_td <- subset(Weekly_Passing,sample_wp_td == TRUE)
test_wp_td <- subset(Weekly_Passing, sample_wp_td == FALSE)

RFM1	<-	randomForest(formula = td ~ tt + cay + agg_percent + lcad + ayts + yds +    int + comp_percent + week, data = train_wp_td	, importance = TRUE)

pred_wp_td <- predict(RFM1,newdata = test_wp_td[-10])


```

